{fairmetrics}: An R package for group fairness evaluation

### 2025-06-02 paper.Rmd
Update paper.Rmd

A simple example of how to use the {fairmetrics} package is illustrated below. The example makes use of the `mimic_preprocessed` dataset, a pre-processed version of the the Indwelling Arterial Catheter (IAC) Clinical Dataset, from the MIMIC-II clinical database^[The raw version of this data is made available by PhysioNet [@goldberger2000physiobank] and can be accessed in the {fairmetrics} package by loading the `mimic` dataset.] [@raffa2016clinical; @raffa2016data]. The dataset consists of 1,776 hemodynamically stable patients with respiratory failure and includes demographic information (patient age and gender), vital signs, laboratory results, whether an IAC was used, and a binary outcome indicating whether the patient died within 28 days of admission.

>>>>

A simple example of how to use the {fairmetrics} package is illustrated below. The example makes use of the `mimic_preprocessed` dataset, a pre-processed version of the the Indwelling Arterial Catheter (IAC) Clinical Dataset, from the MIMIC-II clinical database^[The raw version of this data is made available by PhysioNet [@goldberger2000physiobank] and can be accessed in the {fairmetrics} package by loading the `mimic` dataset.] [@raffa2016clinical; @raffa2016data]. The dataset consists of 1,776 hemodynamically stable patients with respiratory failure and includes demographic information (patient age and gender), vital signs, laboratory results, whether an IAC was used, and a binary outcome indicating whether the patient died within 28 days of hospital admission.
